2.4 PRNT50

### 2024-06-18 2_scripts/2.4 PRNT50.qmd
Update figures for the manuscript.

#### Figure panel

```{r}
# use cowplot package
p09all.upper<-cowplot::plot_grid(p09c + ylab("Proportion") +
                           theme(legend.position='top') +
                           guides(color = guide_legend(nrow = 2)), 
                           p09v0 + xlab ("") + ylab(""), nrow=1,
                           labels = c("A", "B"),  align = "h")
p09all.upper

p09all.lower<-cowplot::plot_grid(
                           NULL,  p09v1 + theme(legend.position="none"), nrow=1,
                           labels = c("", "C"))
p09all.lower

png(file="../4_output/figs/Fig.4 Immunity.png", 
    width=2400, height=2000, res=300)
cowplot::plot_grid(p09all.upper, p09all.lower, nrow=2, rel_heights = c(1, 0.8))
dev.off()
```

@@

## 4.4.3 Check the time gap btw 1st dose and 2nd dose. 
```{r}
APL_vax<-RFD4682_v2_vaxe %>%
  select(ULI, ULI_IDe, DOSE_COUNT, IMMUNIZATION_DATE) %>%
  .[.$DOSE_COUNT==1 | .$DOSE_COUNT==2, ]

@@

summary(as.numeric(APL_vax$time_gap))
```

>>>>

@@

#### 4.4.3 Check the time gap btw 1st dose and 2nd dose. 
```{r}
APL_vax<-RFD4682_v2_vaxe %>%
  select(ULI, ULI_IDe, DOSE_COUNT, IMMUNIZATION_DATE) %>%
  .[.$DOSE_COUNT==1 | .$DOSE_COUNT==2, ]

@@

summary(as.numeric(APL_vax$time_gap))
```
##  4.5 Adding the proportion of each stratum

### Make the plot for three strata

#### The unvaccinated stratum
```{r}
# add proportion of the stratum into the data table
tb_abbsv0<-merge(tb_abbsv0, select(tb_abbsv1, samplemonth, n.all),
      by="samplemonth", all.x=T, all.y=F)
tb_abbsv0<-tb_abbsv0 %>%
  mutate(
    prop.stra = n/n.all
  )
p09v0.lab<-c("APL-Abbott (COI=50)", "APL-Abbott (COI=402)",
             "Proportion of the stratum")

tb_abbsv0_melt<-reshape2::melt(select(tb_abbsv0, -c(2:4,7)), 
                        id.vars = c("samplemonth"),
                        variable.name = "COI",
                        value.name = "prop")

# making the plot
p09v0<-tb_abbsv0_melt %>%
  ggplot(aes(x=samplemonth, y=prop)) +
  geom_point(aes(colour=COI)) +
  geom_line(aes(linetype=COI, colour=COI))  +
  theme_bw() + 
  ylim(c(0,1)) +
  xlab("Time of Sample Collection") + 
  ylab("Proportion")+ 
  scale_colour_manual("", values = c("red", "red", "darkgrey"),
                      labels = p09v0.lab)+
  scale_linetype_manual("", values=c(1,3,3), labels = p09v0.lab) +
  theme(legend.position='top') +
  guides(color = guide_legend(nrow = 2)) +
  ggtitle("Stratum: unvaccinated")
p09v0
```

#### The 1-dose only stratum
```{r}
tb_abbsv1_melt<-reshape2::melt(select(tb_abbsv1, -c(2:4,7)), 
                        id.vars = c("samplemonth"),
                        variable.name = "COI",
                        value.name = "prop")

p09v1<-tb_abbsv1_melt %>%
  ggplot(aes(x=samplemonth, y=prop)) +
  geom_point(aes(colour=COI)) +
  geom_line(aes(linetype=COI, colour=COI))  +
  theme_bw() + 
  ylim(c(0,1)) +
  xlab("Time of Sample Collection") + 
  ylab("Proportion")+ 
  scale_colour_manual("", values = c("red", "red", "darkgrey"),
                      labels = p09v0.lab)+
  scale_linetype_manual("", values=c(1,3,3), labels = p09v0.lab) +
  theme(legend.position='none') +
  guides(color = guide_legend(nrow = 2)) +
  ggtitle("Stratum: 1 dose only")
p09v1
```

#### The 2-dose+ stratum
```{r}
tb_abbsv2<-tb_abbsv2[-1,]

# add proportion of the stratum into the data table
tb_abbsv2<-merge(tb_abbsv2, select(tb_abbsv1, samplemonth, n.all),
      by="samplemonth", all.x=T, all.y=F)
tb_abbsv2<-tb_abbsv2 %>%
  mutate(
    prop.stra = n/n.all
  )
```

```{r}
# melt the data tab
tb_abbsv2_melt<-reshape2::melt(select(tb_abbsv2, -c(2:4,7)), 
                        id.vars = c("samplemonth"),
                        variable.name = "COI",
                        value.name = "prop")

p09v2<-tb_abbsv2_melt %>%
  ggplot(aes(x=samplemonth, y=prop)) +
  geom_point(aes(colour=COI)) +
  geom_line(aes(linetype=COI, colour=COI))  +
  theme_bw() + 
  ylim(c(0,1)) +
  xlab("Time of Sample Collection") + 
  ylab("Proportion")+ 
  scale_colour_manual("", values = c("red", "red", "darkgrey"),
                      labels = p09v0.lab)+
  scale_linetype_manual("", values=c(1,3,3), labels = p09v0.lab) +
  theme(legend.position='none') +
  guides(color = guide_legend(nrow = 2)) +
  ggtitle("Stratum: 2 doses +")
p09v2
```

### merge all four into one figue panel
```{r}
rm(p09v0a, p09v1a, p09v2a)
```

#### Figure panel
```{r}
# use cowplot package
p09.upper<-cowplot::plot_grid(p09c + ylab("Proportion") + xlab ("") +
                           theme(legend.position='top') +
                           guides(color = guide_legend(nrow = 2)), 
                           p09v0 + xlab ("") + ylab(""),
                           labels = c("A", "B"),
                           nrow=1,  align = "h")

p09.lower<-cowplot::plot_grid(p09v1, p09v2 + ylab(""),
                              labels = c("C", "D"),
                              nrow=1,  align = "h")
p09all<-cowplot::plot_grid(p09.upper, p09.lower,
                              labels = c("", ""),
                              nrow=2,  align = "v", rel_heights = c(1,0.8))
p09all

png(file="../4_output/figs/Fig.4 Immunity.png", 
    width=2400, height=2000, res=300)
p09all
dev.off()
```
